Modelling Prehistorical Iconographic Compositions. The \proglang{R} package \pkg{decorr}

### 2020-11-22 article_rvTH15_6.tex
gis_2

\documentclass[article]{jss}

@@

<<preliminaries, echo=FALSE, include=FALSE, cache=FALSE >>=
# options(prompt = "R> ", continue = "+  ", width = 70, useFancyQuotes = FALSE)
library("MASS")
library("extrafont") #;library("ggplot")
library("igraph")
opts_chunk$set(prompt=TRUE, fig.pos = 'H', results='asis', highlight=FALSE)
options(prompt = "R> ", continue = "+  ", width = 70, useFancyQuotes = FALSE)
# options(replace.assign=TRUE, width=90, prompt="R> ")
opts_knit$set(concordance=TRUE, self.contained=FALSE, background = "#FFFFFF")
# knitr::opts_chunk$set(fig.pos = 'H')
loadfonts(device = "win")
@

@@

\Address{
  Thomas Huet\\
  CNRS-UMR 5140 \\
  Archeologie des Societes Mediterraneennes\\
  Universite Paul Valery\\
  route de Mende\\
  Montpellier 34199, France\\
  E-mail: \email{thomashuet7@gmail.com}\\
%  URL: \url{https://eeecon.uibk.ac.at/~zeileis/}
}

\begin{document}
% \SweaveOpts{concordance=TRUE}
% \Sweave2knitr("article_rvTH14_1.Rnw")
% \SweaveOpts{concordance=TRUE}

@@

<<echo=FALSE, message=FALSE, warning=FALSE, fig.pos = 'H', fig.align="center", fig.width=10, fig.height=3, fig.cap="\\label{fig:figs}concatenate of graphical units (GUs) is art">>=
# par(mar=c(0,0,0,0))
g <- graph_from_literal(a-+r, r-+t)
plot(g,
     layout = cbind(seq(-1,1,length.out = gorder(g)), 0),
     vertex.color="white",
     vertex.frame.color="white",
     vertex.size=60,
     vertex.label.cex=1.5,
     vertex.label.color="black",
     vertex.label.family="Courier New",
     edge.arrow.size=.5)
@

@@

<<echo=FALSE, message=FALSE, warning=FALSE, fig.pos = 'H', fig.align="center", fig.width=2, fig.height=2, fig.cap="\\label{fig:figs}Potential spatial relations between GUs.">>=
par(mar=c(0.1,0.1,0.1,0.1) )
ugs <- data.frame(name=c("a","r","t"))
lks <- data.frame(from=c("a", "r", "t"),to=c("r", "t", "a"),type=c("=","=","="))
g <- igraph::graph_from_data_frame(lks, directed=FALSE, vertices= ugs)
plot(g,
     vertex.color="white",
     vertex.frame.color="white",
     vertex.size=80,
     vertex.label.cex=1,
     vertex.label.color="black",
     vertex.label.family="Courier New"
     )
@

@@

The dataframe storing the inventory of decorations is \code{imgs}. The field \code{imgs$idf} is the short name of the decoration, useful during statistical analysis. The primary key of each decoration is the concatenate of \code{imgs$site} and \code{imgs$decor}. These keys will allow joints with the other dataframes (\code{nodes} and \code{edges})\\
%
<<results='asis', echo=FALSE>>=
library("decorr")
library("igraph")
library("magick")
# par(mar=c(0,0,0,0))
imgs <- read.table(system.file("extdata", "imgs.tsv", package = "decorr"),
                   sep="\t", stringsAsFactors = FALSE)
print(xtable::xtable(imgs,
                     caption="The studied corpus, the \\code{imgs.tsv} dataframe",
                     label="Test_table",
                     size=6,
                     align=c(
                       "|p{0.01cm}|",
                       "|p{0.5cm}|",
                       "p{2.5cm}|",
                       "p{2.5cm}|",
                       "p{8.5cm}|")),
      table.placement="H",
      include.rownames=FALSE)
@
%
The \pkg{decorr} package training dataset is composed by four stelaes decorations drawings \citep{DiazGuardamino10} belonging to the so-called 'Warrior stelae' family -- with about 140 stelae -- dated to the Late Bronze Age of SW Iberian peninsula \citep{Celestino01}. At first the drawings dataset can be checked by using the \code{imgs} dataframe and the \pkg{magick} package.
%
<<echo=TRUE, message=FALSE, warning=FALSE, fig.pos = 'H', fig.align="center", fig.width=13, fig.height=13, fig.cap="\\label{fig:figs}Decoration images of the training dataset">>=
# library("magick")
pth <- system.file("extdata", package = "decorr")
imgs <- read.table(system.file("extdata", "imgs.tsv", package = "decorr"),
                   sep="\t", stringsAsFactors = FALSE)
lims <- list()
for(i in 1:nrow(imgs)){
  i1 <- image_read(paste0(pth,"\\",imgs[i,"img"]))
  lbl.txt <- paste0(imgs[i,"idf"],"\n",
                    imgs[i,"site"],"\n",
                    imgs[i,"decor"],"\n",
                    imgs[i,"img"],"\n",
                    image_info(i1)$width,"*",image_info(i1)$height," px")
  i1 <- image_annotate(i1,lbl.txt,location = "northwest",
                       size = 25, color = "red")
  lims[[length(lims)+1]]<- i1
}
out.img <- image_append(c(image_append(c(lims[[1]],lims[[2]])),
                          image_append(c(lims[[3]],lims[[4]]))),
                        stack = TRUE)
plot(out.img)
@
%
To construct a graph overlapping the decoration images listed in the \code{images} dataframe, the first step is to load \code{nodes} and \code{edges} dataframes.
%
<<echo=TRUE>>=
nodes <- read.table(system.file("extdata", "nodes.csv", package = "decorr"),
                    sep=";",stringsAsFactors = FALSE)
edges <- read.table(system.file("extdata", "edges.csv", package = "decorr"),
                    sep=";",stringsAsFactors = FALSE)
@

@@

<<results='asis', echo=TRUE>>=
caption <- "Nodes (from \\code{nodes.csv} dataframe)}"
print(xtable::xtable(head(nodes),
                     caption = caption),
      table.placement="H")
@

@@

<<edgesdf, results='asis', echo=TRUE>>=
caption <- "Edges (from \\code{edges.csv} dataframe)}"
print(xtable::xtable(head(edges),
               caption=caption,
               label="edgesdf"),
      table.placement="H")
@

@@

<<results='asis', echo=TRUE>>=
cm.1 <- subset(nodes, decor == "Cerro Muriano 1" & id == 1)[,c("x","y")]
cm.8 <- subset(nodes, decor == "Cerro Muriano 1" & id == 8)[,c("x","y")]
cat(as.numeric(cm.1),";",as.numeric(cm.8))
@

@@

<<echo=TRUE, message=FALSE, warning=FALSE, fig.pos = 'H', fig.align="center", fig.width=2.5, fig.height=2.5, fig.cap="\\label{fig:figs}Plot of the first graph of the list">>=
# par(mar=c(0.1,0.1,0.1,0.1))
# library("decorr")
# library("magick")
# imgs <- read.table(system.file("extdata", "imgs.tsv", package = "decorr"),
#                       sep="\t", stringsAsFactors = FALSE)
# nodes <- read.table(system.file("extdata", "nodes.csv", package = "decorr"),
#                     sep="\t",stringsAsFactors = FALSE)
# edges <- read.table(system.file("extdata", "edges.csv", package = "decorr"),
#                     sep="\t",stringsAsFactors = FALSE)
lgrph <- list_dec(imgs,nodes,edges,var="type")
plot(lgrph[[1]],
     vertex.color = "orange",
     vertex.frame.color="orange",
     vertex.label.color = "black",
     vertex.size = 8,
     vertex.label.cex = 0.6,
     edge.color = "orange",
     vertex.label.family="Helvetica"
)
@

@@

<<results='asis', echo=TRUE>>=
# library(decorr)
sit <- "Torrejon Rubio" ; dec <- "Torrejon Rubio 1"
nds.df <- read_nds(site = sit, decor = dec, dev = ".tsv",
                   doss = system.file("extdata", package = "decorr"))
eds.df <- read_eds(site = sit, decor = dec, dev = ".tsv",
                   doss = system.file("extdata", package = "decorr"))
print(xtable::xtable(eds.df[1,],
                     caption="first edge of the dataframe",
                     label="Test_table_1",
                     size=7),
      table.placement="H")
@
\end{figure}

@@

<<echo=TRUE, message=FALSE, warning=FALSE, fig.pos = 'H', fig.align="center", fig.width=3, fig.cap="\\label{fig:figs}Torrejon Rubio 1 decoration">>=
# library("decorr")
par(mar=c(0,0,0,0))
sit <- "Torrejon Rubio" ; dec <- "Torrejon Rubio 1"
nds.df <- read_nds(site = sit, decor = dec, dev = ".tsv",
                   doss = system.file("extdata", package = "decorr"))
eds.df <- read_eds(site = sit, decor = dec, dev = ".tsv",
                   doss = system.file("extdata", package = "decorr"))
img.graph <- plot_dec_grph(nds.df = nds.df,
                           eds.df = eds.df,
                           site = sit,
                           decor = dec,
                           doss = system.file("extdata", package = "decorr"),
                           lbl.txt = "type",
                           lbl.size=1.7,
                           shw = c("nodes","edges"))
plot(image_trim(img.graph))
@

@@

<<results='asis', echo=TRUE>>=
# set wd to data folder
# setwd(system.file("extdata", package = "decorr"))
# library("decorr")
g.compar <- list_eds_compar(lgrph,"type")
df.edges.compar <- data.frame(decor.A=c(g.compar[[1]][[1]]$decor,
                                       g.compar[[2]][[1]]$decor,
                                       g.compar[[3]][[1]]$decor,
                                       g.compar[[4]][[1]]$decor,
                                       g.compar[[5]][[1]]$decor,
                                       g.compar[[6]][[1]]$decor),
                              decor.B=c(g.compar[[1]][[2]]$decor,
                                       g.compar[[2]][[2]]$decor,
                                       g.compar[[3]][[2]]$decor,
                                       g.compar[[4]][[2]]$decor,
                                       g.compar[[5]][[2]]$decor,
                                       g.compar[[6]][[2]]$decor))
print(xtable::xtable(df.edges.compar,
                     caption="Pairwise comparisons dataframe between decor.A and decor.B",
                     label="Test_table_1",
                     size=7),
      table.placement="H")
@

@@

<<echo=TRUE, message=FALSE, warning=FALSE, fig.pos = 'H', fig.align="center", fig.height=8, fig.cap="\\label{fig:figs}comparisons between 1 (Cerro Muriano 1) and 4 (Zarza de Montsanchez) decorations">>=
par(mar=c(0,0,0,0))
eds_compar <- plot_eds_compar(g.compar, c(1,4),
                              doss = system.file("extdata", package = "decorr"))
plot(image_trim(image_read(eds_compar)))
@

@@

<<results='asis', echo=TRUE>>=
df.same_edges <- same_eds(lgrph,"type")
caption <- "Number of same edges between all decoration pairwise comparisons"
print(xtable::xtable(df.same_edges,
                     caption = caption,
                     label = "Test_table_2",
                     size = 8,
                     digits = c(0)),
      table.placement="H",
      include.rownames = TRUE)
@

@@

\begin{table}[H]
\begin{minipage}{.45\textwidth}
\centering
<<echo=FALSE,results='asis' >>=
library("xtable")
# library("MASS");library(decorr);library(xtable);library(magick)
# imgs <- read.table(system.file("extdata", "imgs.tsv", package = "decorr"),
#                    sep="\t",stringsAsFactors = FALSE)
# nodes <- read.table(system.file("extdata", "nodes.tsv", package = "decorr"),
#                     sep="\t",stringsAsFactors = FALSE)
# edges <- read.table(system.file("extdata", "edges.tsv", package = "decorr"),
#                     sep="\t",stringsAsFactors = FALSE)
# lgrph <- list_dec(imgs,nodes,edges,"type")
df.same_edges <- same_eds(lgrph,"type")
df.same_nodes<- same_nds(lgrph,"type")
# library("xtable")
print(xtable(df.same_nodes, digits=c(0)),
      floating=FALSE,
      hline.after=NULL)
@
\captionof{table}{Common nodes table}
\end{minipage}
\begin{minipage}{.45\textwidth}
\centering
<<echo=FALSE,results='asis'>>=
print(xtable(df.same_edges, digits=c(0)),
      floating=FALSE,
      hline.after=NULL)
@
\captionof{table}{Common edges table}
\end{minipage}
\end{table}

@@

\begin{figure}[H]
<<echo=TRUE, warning=FALSE>>=
library("matlib")
par(mfrow=c(1,2))
dist.nodes  <- dist(inv(as.matrix(df.same_nodes)))
dist.edges  <- dist(inv(as.matrix(df.same_edges)))
plot(hclust(dist.nodes), hang = -1, main = "common nodes")
plot(hclust(dist.edges), hang = -1, main = "common edges")
@
\end{figure}

@@

<<echo=TRUE, message=FALSE, warning=FALSE, fig.pos = 'H', fig.align="center", fig.cap="\\label{fig:figs}Decoration comparisons between 3 and 4">>=
par(mar=c(0,0,0,0))
par(mfrow=c(2,1))
g.compar <- list_nds_compar(lgrph,"type")
nds_compar.3.4 <- plot_nds_compar(g.compar, c(3,4),
                                  doss = system.file("extdata", package = "decorr"))
plot(image_read(nds_compar.3.4))
g.compar <- list_eds_compar(lgrph,"type")
eds_compar.3.4 <- plot_eds_compar(g.compar, c(3,4),
                              doss = system.file("extdata", package = "decorr"))
plot(image_read(eds_compar.3.4))
@

>>>>

\documentclass[article]{jss}\usepackage{knitr}

@@

@@

\Address{
  Thomas Huet\\
  CNRS-UMR 5140 \\
  Archeologie des Societes Mediterraneennes\\
  Universite Paul Valery\\
  route de Mende\\
  Montpellier 34199, France\\
  E-mail: \email{thomashuet7@gmail.com}\\
%  URL: \url{https://eeecon.uibk.ac.at/~zeileis/}
}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}
% \SweaveOpts{concordance=TRUE}
% \Sweave2knitr("article_rvTH14_1.Rnw")
% \SweaveOpts{concordance=TRUE}

@@

\begin{figure}[H]

{\centering \includegraphics[width=\maxwidth]{figure/unnamed-chunk-1-1}

}

\caption{\label{fig:figs}concatenate of graphical units (GUs) is art}\label{fig:unnamed-chunk-1}
\end{figure}

@@

\begin{figure}[H]

{\centering \includegraphics[width=\maxwidth]{figure/unnamed-chunk-2-1}

}

\caption{\label{fig:figs}Potential spatial relations between GUs.}\label{fig:unnamed-chunk-2}
\end{figure}

@@

The dataframe storing the inventory of decorations is \code{imgs}. The field \code{imgs$idf} is the short name of the decoration, useful during statistical analysis. The primary key of each decoration is the concatenate of \code{imgs$site} and \code{imgs$decor}. These keys will allow joints with the other dataframes (\code{nodes} and \code{edges})\\
%
\begin{kframe}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning: package 'magick' was built under R version 3.6.3}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# Linking to ImageMagick 6.9.9.14\\\#\# Enabled features: cairo, freetype, fftw, ghostscript, lcms, pango, rsvg, webp\\\#\# Disabled features: fontconfig, x11}}\end{kframe}% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Sun Nov 22 13:33:53 2020
\begin{table}[H]
\centering
\begin{tabular}{|p{0.5cm}|p{2.5cm}|p{2.5cm}|p{8.5cm}|}
  \hline
idf & site & decor & img \\ 
  \hline
  1 & Cerro Muriano & Cerro Muriano 1 & Cerro\_Muriano.Cerro\_Muriano\_1.jpg \\ 
    2 & Torrejon Rubio & Torrejon Rubio 1 & Torrejon\_Rubio.Torrejon\_Rubio\_1.jpg \\ 
    3 & Brozas & Brozas & Brozas.Brozas.jpg \\ 
    4 & Zarza de Montanchez & Zarza De Montanchez & Zarza\_de\_Montanchez.Zarza\_De\_Montanchez.jpg \\ 
    5 & Ibahernando & Ibahernando & Ibahernando.Ibahernando.jpg \\ 
   \hline
\end{tabular}
\caption{The studied corpus, the \code{imgs.tsv} dataframe} 
\label{Test_table}
\end{table}

%
The \pkg{decorr} package training dataset is composed by four stelaes decorations drawings \citep{DiazGuardamino10} belonging to the so-called 'Warrior stelae' family -- with about 140 stelae -- dated to the Late Bronze Age of SW Iberian peninsula \citep{Celestino01}. At first the drawings dataset can be checked by using the \code{imgs} dataframe and the \pkg{magick} package.
%
\begin{kframe}
\begin{verbatim}
R> # library("magick")
R> pth <- system.file("extdata", package = "decorr")
R> imgs <- read.table(system.file("extdata", "imgs.tsv", package = "decorr"),
+                     sep="\t", stringsAsFactors = FALSE)
R> lims <- list()
R> for(i in 1:nrow(imgs)){
+    i1 <- image_read(paste0(pth,"\\",imgs[i,"img"]))
+    lbl.txt <- paste0(imgs[i,"idf"],"\n",
+                      imgs[i,"site"],"\n",
+                      imgs[i,"decor"],"\n",
+                      imgs[i,"img"],"\n",
+                      image_info(i1)$width,"*",image_info(i1)$height," px")
+    i1 <- image_annotate(i1,lbl.txt,location = "northwest",
+                         size = 25, color = "red")
+    lims[[length(lims)+1]]<- i1
+  }
R> out.img <- image_append(c(image_append(c(lims[[1]],lims[[2]])),
+                            image_append(c(lims[[3]],lims[[4]]))),
+                          stack = TRUE)
R> plot(out.img)
\end{verbatim}
\end{kframe}\begin{figure}[H]

{\centering \includegraphics[width=\maxwidth]{figure/unnamed-chunk-4-1}

}

\caption{\label{fig:figs}Decoration images of the training dataset}\label{fig:unnamed-chunk-4}
\end{figure}

%
To construct a graph overlapping the decoration images listed in the \code{images} dataframe, the first step is to load \code{nodes} and \code{edges} dataframes.
%
\begin{kframe}
\begin{verbatim}
R> nodes <- read.table(system.file("extdata", "nodes.csv", package = "decorr"),
+                      sep=";",stringsAsFactors = FALSE)
R> edges <- read.table(system.file("extdata", "edges.csv", package = "decorr"),
+                      sep=";",stringsAsFactors = FALSE)
\end{verbatim}
\end{kframe}

@@

\begin{kframe}
\begin{verbatim}
R> caption <- "Nodes (from \\code{nodes.csv} dataframe)}"
R> print(xtable::xtable(head(nodes),
+                       caption = caption),
+        table.placement="H")
\end{verbatim}
\end{kframe}% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Sun Nov 22 13:33:54 2020
\begin{table}[H]
\centering
\begin{tabular}{rl}
  \hline
 & V1 \\ 
  \hline
1 & site	decor	id	type	x	y \\ 
  2 & 1	Cerro Muriano	Cerro Muriano 1	1	personnage	349.814824824793	-298.324408661478 \\ 
  3 & 2	Cerro Muriano	Cerro Muriano 1	2	casque	349.814824824793	-243.98505280916 \\ 
  4 & 3	Cerro Muriano	Cerro Muriano 1	3	lance	238.463685783159	-298.324408661478 \\ 
  5 & 4	Cerro Muriano	Cerro Muriano 1	4	bouclier	446.022208956765	-381.169656108454 \\ 
  6 & 5	Cerro Muriano	Cerro Muriano 1	5	peigne	283.004141399813	-358.008619187794 \\ 
   \hline
\end{tabular}
\caption{Nodes (from \code{nodes.csv} dataframe)}} 
\end{table}

@@

\begin{kframe}
\begin{verbatim}
R> caption <- "Edges (from \\code{edges.csv} dataframe)}"
R> print(xtable::xtable(head(edges),
+                 caption=caption,
+                 label="edgesdf"),
+        table.placement="H")
\end{verbatim}
\end{kframe}% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Sun Nov 22 13:33:54 2020
\begin{table}[H]
\centering
\begin{tabular}{rl}
  \hline
 & V1 \\ 
  \hline
1 & site	decor	a	b	type \\ 
  2 & 1	Cerro Muriano	Cerro Muriano 1	1	4	= \\ 
  3 & 2	Cerro Muriano	Cerro Muriano 1	1	5	= \\ 
  4 & 3	Cerro Muriano	Cerro Muriano 1	3	5	= \\ 
  5 & 4	Cerro Muriano	Cerro Muriano 1	1	2	+ \\ 
  6 & 5	Cerro Muriano	Cerro Muriano 1	1	7	+ \\ 
   \hline
\end{tabular}
\caption{Edges (from \code{edges.csv} dataframe)}} 
\label{edgesdf}
\end{table}

@@

\begin{kframe}
\begin{verbatim}
R> cm.1 <- subset(nodes, decor == "Cerro Muriano 1" & id == 1)[,c("x","y")]
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(e, x, parent.frame()): object 'decor' not found}}\begin{verbatim}
R> cm.8 <- subset(nodes, decor == "Cerro Muriano 1" & id == 8)[,c("x","y")]
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in eval(e, x, parent.frame()): object 'decor' not found}}\begin{verbatim}
R> cat(as.numeric(cm.1),";",as.numeric(cm.8))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in cat(as.numeric(cm.1), "{};"{}, as.numeric(cm.8)): object 'cm.1' not found}}\end{kframe}

@@

\begin{kframe}
\begin{verbatim}
R> # par(mar=c(0.1,0.1,0.1,0.1))
R> # library("decorr")
R> # library("magick")
R> # imgs <- read.table(system.file("extdata", "imgs.tsv", package = "decorr"),
R> #                       sep="\t", stringsAsFactors = FALSE)
R> # nodes <- read.table(system.file("extdata", "nodes.csv", package = "decorr"),
R> #                     sep="\t",stringsAsFactors = FALSE)
R> # edges <- read.table(system.file("extdata", "edges.csv", package = "decorr"),
R> #                     sep="\t",stringsAsFactors = FALSE)
R> lgrph <- list_dec(imgs,nodes,edges,var="type")
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in igraph::graph\_from\_data\_frame(g.edges, directed = FALSE, vertices = g.nodes): the data frame should contain at least two columns}}\begin{verbatim}
R> plot(lgrph[[1]],
+       vertex.color = "orange",
+       vertex.frame.color="orange",
+       vertex.label.color = "black",
+       vertex.size = 8,
+       vertex.label.cex = 0.6,
+       edge.color = "orange",
+       vertex.label.family="Helvetica"
+  )
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot(lgrph[[1]], vertex.color = "{}orange"{}, vertex.frame.color = "{}orange"{}, : object 'lgrph' not found}}\end{kframe}

@@

\begin{kframe}
\begin{verbatim}
R> # library(decorr)
R> sit <- "Torrejon Rubio" ; dec <- "Torrejon Rubio 1"
R> nds.df <- read_nds(site = sit, decor = dec, dev = ".tsv",
+                     doss = system.file("extdata", package = "decorr"))
R> eds.df <- read_eds(site = sit, decor = dec, dev = ".tsv",
+                     doss = system.file("extdata", package = "decorr"))
R> print(xtable::xtable(eds.df[1,],
+                       caption="first edge of the dataframe",
+                       label="Test_table_1",
+                       size=7),
+        table.placement="H")
\end{verbatim}
\end{kframe}% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Sun Nov 22 13:33:54 2020
\begin{table}[H]
\centering
\begin{tabular}{rllrrlrrrr}
  \hline
 & site & decor & a & b & type & xa & ya & xb & yb \\ 
  \hline
9 & Torrejon Rubio & Torrejon Rubio 1 &   6 &   5 & = & 366.70 & -563.14 & 490.12 & -513.24 \\ 
   \hline
\end{tabular}
\caption{first edge of the dataframe} 
\label{Test_table_1}
\end{table}

\end{figure}

@@

\begin{kframe}
\begin{verbatim}
R> # library("decorr")
R> par(mar=c(0,0,0,0))
R> sit <- "Torrejon Rubio" ; dec <- "Torrejon Rubio 1"
R> nds.df <- read_nds(site = sit, decor = dec, dev = ".tsv",
+                     doss = system.file("extdata", package = "decorr"))
R> eds.df <- read_eds(site = sit, decor = dec, dev = ".tsv",
+                     doss = system.file("extdata", package = "decorr"))
R> img.graph <- plot_dec_grph(nds.df = nds.df,
+                             eds.df = eds.df,
+                             site = sit,
+                             decor = dec,
+                             doss = system.file("extdata", package = "decorr"),
+                             lbl.txt = "type",
+                             lbl.size=1.7,
+                             shw = c("nodes","edges"))
R> plot(image_trim(img.graph))
\end{verbatim}
\end{kframe}\begin{figure}[H]

{\centering \includegraphics[width=\maxwidth]{figure/unnamed-chunk-10-1}

}

\caption{\label{fig:figs}Torrejon Rubio 1 decoration}\label{fig:unnamed-chunk-10}
\end{figure}

@@

\begin{kframe}
\begin{verbatim}
R> # set wd to data folder
R> # setwd(system.file("extdata", package = "decorr"))
R> # library("decorr")
R> g.compar <- list_eds_compar(lgrph,"type")
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in lapply(lgrph, function(x) x\$name): object 'lgrph' not found}}\begin{verbatim}
R> df.edges.compar <- data.frame(decor.A=c(g.compar[[1]][[1]]$decor,
+                                         g.compar[[2]][[1]]$decor,
+                                         g.compar[[3]][[1]]$decor,
+                                         g.compar[[4]][[1]]$decor,
+                                         g.compar[[5]][[1]]$decor,
+                                         g.compar[[6]][[1]]$decor),
+                                decor.B=c(g.compar[[1]][[2]]$decor,
+                                         g.compar[[2]][[2]]$decor,
+                                         g.compar[[3]][[2]]$decor,
+                                         g.compar[[4]][[2]]$decor,
+                                         g.compar[[5]][[2]]$decor,
+                                         g.compar[[6]][[2]]$decor))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in data.frame(decor.A = c(g.compar[[1]][[1]]\$decor, g.compar[[2]][[1]]\$decor, : object 'g.compar' not found}}\begin{verbatim}
R> print(xtable::xtable(df.edges.compar,
+                       caption="Pairwise comparisons dataframe between decor.A and decor.B",
+                       label="Test_table_1",
+                       size=7),
+        table.placement="H")
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in xtable::xtable(df.edges.compar, caption = "{}Pairwise comparisons dataframe between decor.A and decor.B"{}, : object 'df.edges.compar' not found}}\end{kframe}

@@

\begin{kframe}
\begin{verbatim}
R> par(mar=c(0,0,0,0))
R> eds_compar <- plot_eds_compar(g.compar, c(1,4),
+                                doss = system.file("extdata", package = "decorr"))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in unlist(listg, recursive = FALSE): object 'g.compar' not found}}\begin{verbatim}
R> plot(image_trim(image_read(eds_compar)))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in image\_read(eds\_compar): object 'eds\_compar' not found}}\end{kframe}

@@

\begin{kframe}
\begin{verbatim}
R> df.same_edges <- same_eds(lgrph,"type")
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in lapply(lgrph, function(x) x\$name): object 'lgrph' not found}}\begin{verbatim}
R> caption <- "Number of same edges between all decoration pairwise comparisons"
R> print(xtable::xtable(df.same_edges,
+                       caption = caption,
+                       label = "Test_table_2",
+                       size = 8,
+                       digits = c(0)),
+        table.placement="H",
+        include.rownames = TRUE)
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in xtable::xtable(df.same\_edges, caption = caption, label = "{}Test\_table\_2"{}, : object 'df.same\_edges' not found}}\end{kframe}

@@

\begin{table}[H]
\begin{minipage}{.45\textwidth}
\centering
\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in lapply(lgrph, function(x) x\$name): object 'lgrph' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in lapply(lgrph, function(x) x\$name): object 'lgrph' not found}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in xtable(df.same\_nodes, digits = c(0)): object 'df.same\_nodes' not found}}\end{kframe}
\captionof{table}{Common nodes table}
\end{minipage}
\begin{minipage}{.45\textwidth}
\centering
\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in xtable(df.same\_edges, digits = c(0)): object 'df.same\_edges' not found}}\end{kframe}
\captionof{table}{Common edges table}
\end{minipage}
\end{table}

@@

\begin{figure}[H]
\begin{kframe}
\begin{verbatim}
R> library("matlib")
R> par(mfrow=c(1,2))
R> dist.nodes  <- dist(inv(as.matrix(df.same_nodes)))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in as.matrix(df.same\_nodes): object 'df.same\_nodes' not found}}\begin{verbatim}
R> dist.edges  <- dist(inv(as.matrix(df.same_edges)))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in as.matrix(df.same\_edges): object 'df.same\_edges' not found}}\begin{verbatim}
R> plot(hclust(dist.nodes), hang = -1, main = "common nodes")
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in hclust(dist.nodes): object 'dist.nodes' not found}}\begin{verbatim}
R> plot(hclust(dist.edges), hang = -1, main = "common edges")
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in hclust(dist.edges): object 'dist.edges' not found}}\end{kframe}
\end{figure}

@@

\begin{kframe}
\begin{verbatim}
R> par(mar=c(0,0,0,0))
R> par(mfrow=c(2,1))
R> g.compar <- list_nds_compar(lgrph,"type")
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in utils::combn(1:length(lgrph), 2): object 'lgrph' not found}}\begin{verbatim}
R> nds_compar.3.4 <- plot_nds_compar(g.compar, c(3,4),
+                                    doss = system.file("extdata", package = "decorr"))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in plot\_nds\_compar(g.compar, c(3, 4), doss = system.file("{}extdata"{}, : object 'g.compar' not found}}\begin{verbatim}
R> plot(image_read(nds_compar.3.4))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in image\_read(nds\_compar.3.4): object 'nds\_compar.3.4' not found}}\begin{verbatim}
R> g.compar <- list_eds_compar(lgrph,"type")
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in lapply(lgrph, function(x) x\$name): object 'lgrph' not found}}\begin{verbatim}
R> eds_compar.3.4 <- plot_eds_compar(g.compar, c(3,4),
+                                doss = system.file("extdata", package = "decorr"))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in unlist(listg, recursive = FALSE): object 'g.compar' not found}}\begin{verbatim}
R> plot(image_read(eds_compar.3.4))
\end{verbatim}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in image\_read(eds\_compar.3.4): object 'eds\_compar.3.4' not found}}\end{kframe}
